---
title: "CodeBook"
author: "Daniel dela Torre"
date: "11/1/2017"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk("/Users/delatorredm/Getting_and_Cleaning_Data/run_analysis.R")
```

## CodeBook for tidy.txt

This codebook accompanies "tidy.txt" which is produced from the original dataset taken from <http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones>.

The following enumerate the datasets included.

### ID
* Subject - each subject has a unique integer ID
* Activity - the following are the codes for each activity

```{r chunk1}
activity
```

### FEATURES

*The following description was taken from the **features_info.txt** from the original dataset*

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerk-XYZ and tBodyGyroJerk-XYZ). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag). 

Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAcc-XYZ, fBodyAccJerk-XYZ, fBodyGyro-XYZ, fBodyAccJerkMag, fBodyGyroMag, fBodyGyroJerkMag. (Note the 'f' to indicate frequency domain signals). 

These signals were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

For the purpose of this exercise, only the *mean* and *standard deviation* statistics were used.

The final list of features used are enumerated below.

```{r chunk2}
featuresLabels
```